---
title: "2018 Technical Reconsideration Draft RIA Results"
date: "September, 2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(here)
library(knitr)
source(here("scripts", "setup.R"))

knitr::opts_chunk$set(
  echo = FALSE
  )

# scenario data in scope from calling env
if (!exists("scn_comps")) stop("Please render tables by running analysis script.")

#proposed option is set in analysis script
scn_comp <- scn_comps[[prop_opt]]

# set some knitr options
options(knitr.table.format = 'html')

wb <- loadWorkbook("../output/xlsx/tables_tech_reconsideration.xlsx")

```

## Introduction

This document provides tables for the OOOOa 2018 Technical Reconsideration RIA. This is an html document which can be viewed in your browser. Matching xlsx output tables are also produced.

**Technical note:** this document is produced by rendering with `rmarkdown::render()` in R.

```{r}
#Summary Output Sheets "raw" totals by year
write_tbl_to_xlsx(scn_summ_list[[1]], wb, "Option1")
write_tbl_to_xlsx(scn_summ_list[[2]], wb, "Option2")
write_tbl_to_xlsx(scn_summ_list[[3]], wb, "Option3")
write_tbl_to_xlsx(scn_summ_list[[4]], wb, "AnnComps")
write_tbl_to_xlsx(scn_summ_list[[5]], wb, "QuarterlyComps")
```


## Overview of Affected Facilities

Affected facilities for the purpose of RIA tables are facilities which make changes in their controls as a result of this reconsideration action. In the case of this framework, this corresponds to differences in the total counts of model-plant fate in particular years. 

Incrementally affected facilities means that vintage == year, e.g., facilities new/modified in a particular year that are affected.


```{r tbl_fac_affected}
tbl_fac_affected <- scn_comp_table(scn_comp,
              var_list = list("fac_affected"),
              row_detail = "total",
              show_years = 2019:2025)

tbl_incr_affected <- scn_comp %>%
  filter(year == vintage) %>%
  scn_comp_table(var_list = list("fac_affected"),
                 row_detail = "total",
                 show_years = 2019:2025) %>%
  rename(incr_affected = fac_affected)

tbl_affected <- left_join(tbl_incr_affected,   tbl_fac_affected, by = "year")

tbl_affected %>%
  mutate_at(.vars = c("incr_affected", "fac_affected"), funs(rndmark(., 2))) %>%
  kable(caption = "Affected Facility Overview Compared to 2018 Baseline") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F) %>%
  collapse_rows(columns = 1)

tbl_affected %>%
  write_tbl_to_xlsx(wb, "fac_affected")
```


# Emissions

```{r tbl_emissions}

tbl_emissions <- scn_comp_table(scn_comp,
               var_list = list("Methane", "VOC", "HAP", "CH4_CO2e"),
               row_detail = "total",
               show_years = 2014:2025) #%>%
  

tbl_emissions %>%
  mutate_at(.vars = c("Methane", "VOC", "HAP", "CH4_CO2e"), 
            funs(rndmark(., 2))) %>%
  kable(caption = "Change in Emissions for the Proposed Reconsideration Option compared to 2018 Baseline, by year") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F) %>%
  collapse_rows(columns = 1)

tbl_emissions %>% 
  
  write_tbl_to_xlsx(wb, "emissions")

```


```{r tbl_gas}

tbl_gas <- scn_comp_table(scn_comp,
               var_list = list("gas_capture", "gas_revenue"),
               row_detail = "total",
               show_years = 2019:2025)


tbl_gas %>%
  mutate(gas_capture = rndmark(gas_capture, 2),
         gas_revenue = currency(gas_revenue, 2)) %>%
  kable(caption = "Change in Natural Gas Recovery (Mcf) for the Proposed Reconsideration Option Compared to 2018 Baseline, by year") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F)

tbl_gas %>%
  write_tbl_to_xlsx(wb, "gas_revenue")

```

```{r tbl_costs}

tbl_costs <- scn_comp_table(scn_comp,
               var_list = list("capital_cost", "ann_7", "gas_revenue", "ann_7_wgas"),
               row_detail = "total",
               show_years = 2019:2025)


tbl_costs %>%
  mutate_at(c("capital_cost", "ann_7", "gas_revenue", "ann_7_wgas"),
            .funs = funs(Mdollar(.))) %>%
  kable(caption = "Change in Natural Gas Recovery (Mcf) for the Proposed Reconsideration Option Compared to 2018 Baseline, by year")

tbl_costs %>%
  write_tbl_to_xlsx(wb, "costs")

```


```{r comp_alts}

comp_alts <- scn_combo %>%
  filter(pol_scn %in% 
           c("1.Option 1", "2.Option 2", "3.Option 3")) %>%
  filter(year %in% c(2020,2025)) %>%
  group_by(pol_scn, year) %>%
  summarize_at(.vars = vars("Methane", "VOC", "gas_capture", 
                            "capital_cost", "ann_7", "ann_7_wgas"),
               .funs = funs(sum(., na.rm = TRUE))) %>%
  ungroup()

var_order <- c("Methane", "VOC", "gas_capture", "capital_cost", "ann_7", "ann_7_wgas")

comp_alts_vert <- comp_alts %>%
  mutate_at(c("Methane", "VOC", "gas_capture"), funs(rndmark(., 2))) %>%
  mutate_at(c("capital_cost", "ann_7", "ann_7_wgas"), funs(Mdollar(., 2))) %>%
  
  gather(var, value, "Methane", "VOC", "gas_capture", 
                            "capital_cost", "ann_7", "ann_7_wgas") %>%
  spread(pol_scn, value) %>% 
  mutate(var = factor(var, levels = var_order)) %>%
  arrange(year, var)

comp_alts_vert %>%
  kable(caption = "Comparison of Regulatory Alternatives to 2018 Baseline, 2020 and 2025") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F) %>%
  collapse_rows(c(1))

comp_alts %>%
  
  gather(var, value, "Methane", "VOC", "gas_capture", 
                            "capital_cost", "ann_7", "ann_7_wgas") %>%
  spread(pol_scn, value) %>% 
  mutate(var = factor(var, levels = var_order)) %>%
  arrange(year, var) %>%
  
  write_tbl_to_xlsx(wb, "comp_alts")

```


```{r pre2016}

tbl_pre2016 <- scn_pre2016_combo %>%
  filter(year %in% c(2020, 2025)) %>%
  group_by(year, pol_scn) %>%
  summarize_at(.vars = vars("fac_affected", "Methane", "VOC", "capital_cost", "ann_7_wgas"),
               .funs = funs(sum(., na.rm = TRUE))) %>%
  ungroup()

tbl_pre2016 %>%
 kable(format.args = list(big.mark = ',', scientific = FALSE))

tbl_pre2016 %>% write_tbl_to_xlsx(wb, "pre2016")

```


```{r costs_dr}

costs_dr <- scn_comp_table(scn_comp,
               var_list = list("ann_7", "gas_revenue", "ann_7_wgas", "ann_3", "ann_3_wgas"),
               row_detail = "total",
               show_years = 2019:2025) %>%
  
  mutate(gas_rev2 = gas_revenue) %>%
  select(year, ann_7, gas_revenue, ann_7_wgas, ann_3, gas_rev2, ann_3_wgas)
  

costs_dr %>%
  mutate_at(vars(-year), funs(Mdollar(., 2))) %>%
  kable(caption = "Undiscounted Annualized Cost Changes using 3 and 7 Percent Discount Rates Compared to 2018 Baseline (million 2016$)")

costs_dr %>%
  write_tbl_to_xlsx(wb, "discount_rate")

```

```{r detail_tabs}

opt_yr_combo <- crossing(opt = 1:3, year = c(2020, 2025)) %>%
  mutate(optname = case_when(
    opt == 1 ~ "1.Option 1",
    opt == 2 ~ "2.Option 2",
    opt == 3 ~ "3.Option 3"
    )
  ) %>% select(opt, optname, year)


det_tab <- pmap_chr(opt_yr_combo, ~glue("Detail_Opt{..1}_{..3}"))

tabfun <- function(scn_combo, opt, optname, year) {
  scn_comp <- scn_combo %>%
    filter(pol_scn == optname) %>%
    select(-pol_scn)
  
  maintab <- scn_comp_table(scn_comp,
              var_list = list("fac_affected", "Methane", "VOC", "HAP", "CH4_CO2e", "capital_cost","annual_cost", "gas_revenue", "ann_7_wgas"),
              row_detail = "source",
              show_years = c(year)) 
  
  tottab <- scn_comp_table(scn_comp,
              var_list = list("fac_affected", "Methane", "VOC", "HAP", "CH4_CO2e", "capital_cost","annual_cost", "gas_revenue", "ann_7_wgas"),
              row_detail = "total",
              show_years = c(year)) %>%
    mutate(year = "Total")
  
  result <- bind_rows(maintab, tottab) #%>%
    
  result
}



det_tabs <- pmap(opt_yr_combo, ~tabfun(scn_combo, ..1, ..2, ..3))

walk2(det_tabs, det_tab, ~write_tbl_to_xlsx(.x, wb, .y))

kabletab <- function(df, cap) {
  df %>%
    mutate_at(c("fac_affected", "Methane", "VOC", "HAP", "CH4_CO2e"),
              funs(rndmark(., 2))) %>%
    mutate_at(c("capital_cost", "ann_7_wgas"),
              funs(currency(., 2))) %>%
    kable(caption = cap) %>%
    kable_styling(bootstrap_options = c("condensed"), full_width = F) %>%
    collapse_rows(c(1,2))
}   

det_names <- pmap_chr(opt_yr_combo, ~glue("Detail of Affected Units, Option {..1},  {..3}"))

kabletab(det_tabs[[1]], det_names[[1]])
kabletab(det_tabs[[2]], det_names[[2]])
kabletab(det_tabs[[3]], det_names[[3]])
kabletab(det_tabs[[4]], det_names[[4]])
kabletab(det_tabs[[5]], det_names[[5]])
kabletab(det_tabs[[6]], det_names[[6]])

```

```{r eav_undiscounted}
cost_undisc_7 <- table_cost_disc_pv_eav(scn_comp, .07, list("capital_cost", "annual_cost", "ann_r", "gas_revenue", "ann_r_wgas"), disc_flag = FALSE)

write_tbl_to_xlsx(cost_undisc_7, wb)

cost_undisc_3 <- table_cost_disc_pv_eav(scn_comp, .03, list("capital_cost", "annual_cost", "ann_r", "gas_revenue", "ann_r_wgas"), disc_flag = FALSE)

write_tbl_to_xlsx(cost_undisc_3, wb)
```

```{r eav_disc}
cost_disc_7 <- table_cost_disc_pv_eav(scn_comp, .07, list("capital_cost", "annual_cost", "ann_r", "gas_revenue", "ann_r_wgas"))

write_tbl_to_xlsx(cost_disc_7, wb)

cost_disc_3 <- table_cost_disc_pv_eav(scn_comp, .03, list("capital_cost", "annual_cost", "ann_r", "gas_revenue", "ann_r_wgas"))

write_tbl_to_xlsx(cost_disc_3, wb)
```

```{r pv_eav_combo}
totals_combo <- scn_combo %>%
  filter(pol_scn %in% 
           c("1.Option 1", "2.Option 2", "3.Option 3")) %>%
  
  group_by(pol_scn) %>%
  summarize_at(.vars = vars("Methane", "VOC", "gas_capture"),
               .funs = funs(sum(., na.rm = TRUE))) %>%
  gather(var, value, Methane, VOC, gas_capture) %>%
  spread(pol_scn, value) %>%
  mutate(vartype = "Total")

pv_combo <- scn_combo %>%
  filter(pol_scn %in% 
           c("1.Option 1", "2.Option 2", "3.Option 3")) %>%
  
  group_by(pol_scn, year) %>%
  summarize_at(vars("capital_cost", "ann_7", "ann_7_wgas"), 
               funs(sum(.))) %>%
  summarize_at(.vars = vars("capital_cost", "ann_7", "ann_7_wgas"),
               .funs = funs( sum(npv_xy_pmts(as.numeric(year), ., .07, 2016)) ))

eav_combo <- pv_combo %>%
  mutate_at(.vars = vars("capital_cost", "ann_7", "ann_7_wgas"),
            .funs = funs(equiv_annualized_value(., 7, .07, 0)))

pv_eav_combo_partial <- bind_rows(
  mutate(pv_combo, vartype = "PV"),
  mutate(eav_combo, vartype = "EAV")
) %>%
  gather(var, value, capital_cost, ann_7, ann_7_wgas) %>%
  spread(pol_scn, value)

pv_eav_combo <- bind_rows(
  totals_combo,
  pv_eav_combo_partial
) %>%
  mutate(vartype = factor(vartype, levels = c("Total", "PV", "EAV"))) %>%
  mutate(var = factor(var, levels = c("Methane", "VOC", "gas_capture", "capital_cost", "ann_7", "ann_7_wgas"))) %>%
  arrange(vartype, var) %>%
  select(var, vartype, everything())

pv_eav_combo
write_tbl_to_xlsx(pv_eav_combo, wb)
```

```{r dr_pv_eav}
dr_pv_eav <- bind_cols(
  table_cost_disc_pv_eav(scn_comp, .07, list("ann_r", "gas_revenue", "ann_r_wgas")),
  table_cost_disc_pv_eav(scn_comp, .03, list("ann_r", "gas_revenue", "ann_r_wgas"))
)

dr_pv_eav
write_tbl_to_xlsx(dr_pv_eav, wb)
```



```{r}
saveWorkbook(wb, "../output/xlsx/tables_tech_reconsideration.xlsx", overwrite = TRUE)
```


